Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-10-14 doc/JFLA2022/paper.tex
avoid two "formalization" in the same sentence

In order to prove formally that the length of the
kind of hydra battles we consider is not given by any primitive recursive function, we chose to use a formalization of primitive recursive functions that was originally part of Russell O'Connor's contribution on G\"{o}del's first incompleteness theorem~\cite{OConnor05, Goedel}.
For this purpose, and above all in consideration of the scientific interest of this contribution, we decided to host and maintain O'Connor's work in \community.

>>>>

In order to prove formally that the length of the
kind of hydra battles we consider is not given by any primitive recursive function, we chose to use a formalization of primitive recursive functions that was originally part of Russell O'Connor's formal proof of G\"{o}del's first incompleteness theorem~\cite{OConnor05, Goedel}.
For this purpose, and above all in consideration of the scientific interest of this contribution, we decided to host and maintain O'Connor's work in \community.
